%-------------------------
% Resume in Latex
% Author : Prashant Singh
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

\pdfgentounicode=1

\newcommand{\resumeItem}[1]{\item\small{{#1 \vspace{-2pt}}}}
\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}
\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}
\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}

%-------------------------------------------
\begin{document}

%----------HEADING----------
\begin{center}
    \textbf{\Huge \scshape Prashant Singh} \\ \vspace{4pt}
    \small +91-7318536221 $|$ \href{mailto:prashant070800@gmail.com}{\underline{prashant070800@gmail.com}} $|$ 
    \href{https://www.linkedin.com/in/prashant0607/}{\underline{linkedin.com/in/prashant0607}} $|$
    \href{https://github.com/prashant070800}{\underline{github.com/prashant070800}}
\end{center}

%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Institute of Engineering and Technology, Lucknow}{8.0 GPA}
      {B.Tech in Electronics and Communication Engineering}{Aug 2018 -- May 2022}
  \resumeSubHeadingListEnd

%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart

\resumeSubheading
  {Software Engineer}{JAXL}{Python, Django, C/C++, SQL, Linux}{Aug 2024 -- Present}
    \resumeItemListStart
    \resumeItem{Developed a **Shopify Integration Engine** utilizing OAuth 2.0 and Webhook subscriptions to trigger automated telecom workflows based on e-commerce events.}
      \resumeItem{Engineered an **Abandoned Cart Recovery** system and **Order Confirmation** module that automatically initiates voice calls/SMS upon detecting specific Shopify webhooks.}
      \resumeItem{Implemented a robust **Webhook Handler** to process high-volume events (Carts, Orders, Bulk Operations) with secure **HMAC validation** and idempotent processing.}
      \resumeItem{Engineered a secure \textbf{Peer-to-Peer (P2P) Messaging} layer using \textbf{Diffie-Hellman (DH) key exchange} and Fernet (AES) for end-to-end encrypted organization communication.}
      \resumeItem{Implemented a "Digital Envelope" encryption strategy, where messages are symmetrically encrypted and the session keys are securely wrapped using derived \textbf{DH shared secrets}.}
      \resumeItem{Developed thread-safe key generation workflows utilizing \textbf{Fortuna-based secure random} generators and Django's \textbf{transaction.atomic} to prevent race conditions during public key distribution.}
      \resumeItem{Architected a high-scale \textbf{Call Campaign Engine} supporting Manual, IVR, and AI-driven conversational calling modules with decoupled agent execution.}
      \resumeItem{Engineered the campaign lifecycle infrastructure, including automated retry logic, role-based permissions, and comprehensive analytical report generation.}
    \resumeItemListEnd

\resumeSubheading
  {Software Engineer}{Infosys}{Python, Flask, Angular, GCP, SQL}{Aug 2022 -- Aug 2024}
    \resumeItemListStart
        \resumeItem{Developed a high-performance \textbf{RAG API} using Flask and \textbf{Milvus vector database}, achieving sub-second document retrieval.}
        \resumeItem{Optimized Large Language Model (LLM) data pipelines by implementing concurrent processing in Python, reducing dataset loading times.}
        \resumeItem{Built and deployed containerized solutions on \textbf{Linux-based GCP environments} leveraging Docker for smart city infrastructure.}
        \resumeItem{Refactored database schemas and tuned complex SQL queries to eliminate performance bottlenecks in production applications.}
    \resumeItemListEnd

\resumeSubheading
  {Software Engineer Intern}{Jaxl Innovations Private Limited}{Python, Django, C/C++}{Apr 2022 -- Jul 2022}
    \resumeItemListStart
        \resumeItem{Implemented secure payment processing via Apple Pay, ensuring full compliance with \textbf{PCI-DSS} API workflows.}
        \resumeItem{Enhanced administrative efficiency by customizing the Django admin interface and implementing indexed queries for faster data visualization.}
    \resumeItemListEnd

  \resumeSubHeadingListEnd

%-----------PROJECTS-----------
\section{Projects}
    \resumeSubHeadingListStart
      \resumeProjectHeading
          {\textbf{Vargi-Bot} $|$ \emph{ROS, Python, C++, OpenCV, MQTT, Linux}}{}
          \resumeItemListStart
            \resumeItem{Developed a 3D warehouse simulation using ROS and Gazebo, featuring a robotic arm controlled by \textbf{multi-threaded perception algorithms}.}
            \resumeItem{Integrated OpenCV-based computer vision for real-time object classification, reducing sorting latency through optimized image processing.}
            \resumeItem{Established a real-time monitoring system using \textbf{MQTT} to sync robotic telemetry with Google Sheets and automated email alerts.}
          \resumeItemListEnd
    \resumeSubHeadingListEnd

%-----------TECHNICAL SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages}{: C/C++, Python, JavaScript, HTML/CSS, SQL} \\
     \textbf{Frameworks \& Tools}{: Django, Flask, Angular, SageMaker, ROS, Milvus, Docker, Twilio/Plivo/Exotel} \\
     \textbf{Concepts}{: Multi-threading, Call Campaigns, REST APIs, Vector Search, RAG, IVR Workflows, AI Agents} \\
     \textbf{Platforms}{: Linux, GCP, Git}
    }}
 \end{itemize}

\end{document}